---
title: "Homework 1"
author: Mufeng Xu
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character and factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, factor_vec))) * pull(prob1_df, samp)
```


## Problem 2

Load the dataset

```{r}
data("penguins", package = "palmerpenguins")
```

Finding important variables, size of the dataset, the mean flipper length

```{r}
colnames(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

the penguins dataset has 8 columns and 344 rows, and its important variables' names include: "species" ,"island","bill_length_mm", "bill_depth_mm","flipper_length_mm" "body_mass_g", "sex", "year". By skipping the NA, I found the mean flipper length is 200.9152 mm.

Load library(ggplot2)

```{r}
library(ggplot2)
```

Make a scatterplot of flipper_length_mm over bill_length_mm, and color coded by species

```{r}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, na.rm = TRUE, color=species))+geom_point()
```

Save the plot as pdf

```{r}
ggsave(file="penguins.pdf")
```


